Oracle Bone Character Recognition\\ with CNN and Template Matching

### 2019-12-15 2-oracle/report/paper.tex
write abstract, title, author, and keywords

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Bare Demo of IEEEtran.cls for Journals}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
	John~Doe,~\IEEEmembership{Fellow,~OSA,}
	and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
	\thanks{M. Shell is with the Department
		of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
		GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
	\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
	\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
	The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
	IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Oracle Bone Character Recognition\\ with CNN and Template Matching}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{
	Zhongye~Wang,~\IEEEmembership{SJTU,}
	Jinyu~Li,~\IEEEmembership{SJTU,}
	Xiaoyi~Bao,~\IEEEmembership{SJTU,}
	Shangning~Xu,~\IEEEmembership{SJTU,}
	and Chenxuan~Li,~\IEEEmembership{SJTU}
}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
	In this project, we tackle the task of oracle bone character detection based on the dataset created in class.
	Due to the limit size of dataset, we first augment data with affine transforms and noise transforms to obtain a larger and more robust dataset.
	We then apply a simple CNN and template matching to implement models that can distinguish bone characters between micro categories (40 classes) and macro categories (10 classes).
	We examine models using our homebrew bone character dataset and find the optimal models for micro and macro category classification tasks.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
	Oracle bone character recognition, CNN, template matching, data augmentation.
\end{IEEEkeywords}
